Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-11-02 paper/paper.qmd
Modify Measurement part

The dataset used in this analysis originates from @fivethirty, a trusted source known for its rigorous methodology in collecting and aggregating polling data to represent public opinion accurately. To maintain data integrity and ensure a high standard of reliability, only polls meeting stringent quality criteria are included in the dataset. Specifically, each poll must disclose important information, including the pollster’s name, the exact dates of the survey, the sample size, and the full methodological details. These details encompass the polling medium (e.g., phone, online), use of verified voter files, demographic weighting criteria, and any adjustments applied to reflect a representative sample.

Polls are rigorously verified, and those that do not meet these requirements are excluded from the dataset. For instance, polls categorized as nonscientific, those that merge data from multiple unrelated sources, and those conducted by hobbyists or unverified entities are filtered out to prevent data quality compromise.

Once verified as credible, polls are incorporated into the FiveThirtyEight database. These polls then contribute to polling averages, forecast models, and political analysis, all of which rely on high-quality, reliable public opinion data. This careful selection process ensures that the dataset reflects a thorough and detailed view of public sentiment, accurately capturing behavioral trends and preferences over time.

>>>>

In this analysis, the goal is to convert individual polling data, which reflects voter sentiment before Election Day, into an estimate of the overall electoral support for each candidate. This process involves systematically capturing public opinion about voting intentions and translating it into structured data that can reliably forecast electoral college outcomes.

The dataset originates from @fivethirty, a trusted source known for its rigorous standards in polling data collection. Only polls meeting specific quality criteria are included, ensuring that data represents a broad cross-section of likely voters across the U.S. Each poll must disclose essential details, including the pollster’s name, survey dates, sample size, and methodological information. This transparency in methodology includes aspects like the polling medium (phone, online), use of voter files, demographic weighting, and any adjustments made to reflect a representative sample. These steps help ensure that the recorded data accurately captures respondents' voting intentions.

Once these polls pass quality checks, they are integrated into the FiveThirtyEight database, where they contribute to aggregated polling averages and forecast models. Poll results are recorded as percentages reflecting the level of support for each candidate, essentially quantifying voter sentiment. However, moving from these individual opinions to a reliable state-by-state and national forecast requires addressing inherent challenges, such as demographic imbalances and geographic biases. To mitigate these, demographic weights are applied, aligning sample composition with actual population distributions.

The measurement approach also includes recency adjustments to account for the time since each poll was conducted, as opinions can shift rapidly closer to Election Day. This approach, combined with selective inclusion criteria, ensures that the dataset reflects a consistent and structured view of voter sentiment across various demographic and regional groups, bridging the gap between initial polling data and final election predictions.
